Experience Report: Distributed Computing for the Common Man

### 2010-03-25 doc/icfp-2010/main.tex
mapreduce -> factory
*** empty log message ***

\authorinfo{Jean-Christophe Filli\^{a}tre}
           {CNRS, LRI, Univ Paris-Sud, Orsay F-91405\\
            INRIA Saclay - Île-de-France, ProVal, Orsay, F-91893}
           {filliatr@lri.fr}
\authorinfo{Kalyan Krishnamani}
           {INRIA Saclay - Île-de-France, ProVal, Orsay, F-91893}
           {kalyan@lri.fr}

>>>>

\authorinfo{Jean-Christophe Filli\^{a}tre}
           {CNRS, LRI, Univ Paris-Sud, Orsay F-91405\\
            INRIA Saclay -- \^Ile-de-France, ProVal, Orsay, F-91893}
           {filliatr@lri.fr}
\authorinfo{Kalyan Krishnamani}
           {INRIA Saclay -- \^Ile-de-France, ProVal, Orsay, F-91893}
           {kalyan@lri.fr}
